AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
at results and discussion

\subsection{Peer validation and peer pressure}

No set bosses or leaders are required in an ideal aplication the AA methodology;
in practice the role of bosses basically disappears or is greatly lightened --
hence the name Algorithmic \emph{Autoregulation} and other implicit
interpretations to the AA acronym and symbol. The primary mechanism to achieve
AA is peer coordination and social behavior, be it deliberate or implicit. In
order to prevent spamming and to improve the overall quality of AA reports, each
AA session must be validated by another developer. More specifically, all
reports are read by someone that will mark them as `valid' or `invalid' and may
optionally write commentaries about the specific session and quality of
micrologs. The developer in charge of validating any given session is randomly
assigned by the AA Web server, which sends an email to the chosen developer with
an URL to a validation interface.

>>>>

\subsection{Peer validation}

No set bosses or leaders are required in an ideal aplication the AA methodology;
in practice, the role of bosses basically disappears or is greatly alleviated --
hence the name Algorithmic \emph{Autoregulation} and other implicit
interpretations to the AA acronym and symbol. The primary mechanism to achieve
AA is peer coordination and social behavior, be it deliberate or implicit. In
order to prevent spamming and to improve the overall quality of AA reports, each
AA session must be validated by another developer. More specifically, all
reports are read by someone that will mark them collectively as `valid' or
`invalid' and may optionally write commentaries about the specific session and
quality of micrologs. The developer in charge of validating any given session is
randomly assigned by the AA Web server, which sends an email to the chosen
developer with an URL to a validation interface.

Peer validation also helps in making decentralized collaboration more cohesive
by encouraging members to be minimally aware of peer activities, even when these
are not immediately useful for accomplishing the task at hand.  We have observed
that decentralized teamwork can get so efficient at actual production that 
the team gets short-sighted in terms of coordination: non-communicating
subteams can get formed in practice if care is not taken, causing a
fragmentation of the collective. Peer validation is one way to help avoid
fragmentation and is an essential mechanism of decentralized team autoregulation.
